Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech

### 2021-03-30 RR_manuscript/Draft_RR.Rmd

These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e. after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
The unpublished study we took the data from aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
In the following section we introduce the research question and the experimental procedure of said study, and we describe the dataset as it was given to the analysts.

@@

The two sentence prompts were used to create a focus contrast between the competitor and the target object.
If the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the narrow focus is on the noun (the Noun Focus condition, NF).
If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the narrow focus is on the color adjective (the Adjective Focus condition, AF).
If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), the narrow focus is on the whole noun phrase (the Adjective/Noun Focus condition, ANF).
The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
Crucially, the color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
The combinations were either typical (e.g. *orange mandarin*), medium typical (e.g. *green tomato*), or atypical (e.g. *yellow cherry*), as established by a norming study that was conducted prior to the production experiment just described.^[A detailed description of the norming study, with a more in-depth description of this production study can be found in `methods_norm_prod.pdf` at (temporary link) <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]
Each subject produced 15 critical trials (NF condition).
Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total of 900 ($15 \times 2 \times 30$ participants) spoken utterances.

>>>>

These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e. after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
The data set derives from the unpublished research project *Prosodic encoding of redundant referring expressions*, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.
In the following section we introduce the research question and the experimental procedure of said project, and we describe the resulting data set as used in the current study.

@@

The two sentence prompts were used to create a focus contrast between the competitor and the target object.
If the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the narrow focus is on the noun (the Noun Focus condition, NF).
If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the narrow focus is on the color adjective (the Adjective Focus condition, AF).
If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), the narrow focus is on the whole noun phrase (the Adjective/Noun Focus condition, ANF).
The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
Crucially, the color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
The combinations were either typical (e.g. *orange mandarin*), medium typical (e.g. *green tomato*), or atypical (e.g. *yellow cherry*), as established by a norming study that was conducted prior to the production experiment just described.^[A detailed description of the norming and production studies from the *Prosodic encoding of redundant referring expressions* project, which was given to the analysts with the data set, can be found in `methods_norm_prod.pdf` at (temporary link) <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]
Each subject produced 15 critical trials (NF condition).
Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total of 900 ($15 \times 2 \times 30$ participants) spoken utterances.

### 2021-03-30 RR_manuscript/Draft_RR.tex

These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
The unpublished study we took the data from aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
In the following section we introduce the research question and the experimental procedure of said study, and we describe the dataset as it was given to the analysts.

@@

The two sentence prompts were used to create a focus contrast between the competitor and the target object.
If the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the narrow focus is on the noun (the Noun Focus condition, NF).
If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the narrow focus is on the color adjective (the Adjective Focus condition, AF).
If both the color and the object differ (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the narrow focus is on the whole noun phrase (the Adjective/Noun Focus condition, ANF).
The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
Crucially, the color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{green tomato}), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment just described.\footnote{A detailed description of the norming study, with a more in-depth description of this production study can be found in \texttt{methods\_norm\_prod.pdf} at (temporary link) \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}
Each subject produced 15 critical trials (NF condition).
Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total of 900 (\(15 \times 2 \times 30\) participants) spoken utterances.

>>>>

These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
The data set derives from the unpublished research project \emph{Prosodic encoding of redundant referring expressions}, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.
In the following section we introduce the research question and the experimental procedure of said project, and we describe the resulting data set as used in the current study.

@@

The two sentence prompts were used to create a focus contrast between the competitor and the target object.
If the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the narrow focus is on the noun (the Noun Focus condition, NF).
If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the narrow focus is on the color adjective (the Adjective Focus condition, AF).
If both the color and the object differ (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the narrow focus is on the whole noun phrase (the Adjective/Noun Focus condition, ANF).
The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
Crucially, the color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{green tomato}), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment just described.\footnote{A detailed description of the norming and production studies from the \emph{Prosodic encoding of redundant referring expressions} project, which was given to the analysts with the data set, can be found in \texttt{methods\_norm\_prod.pdf} at (temporary link) \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}
Each subject produced 15 critical trials (NF condition).
Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total of 900 (\(15 \times 2 \times 30\) participants) spoken utterances.
